\namesection{Christian}{Merx}{Software Engineering Manager}
{\contactline{}{}{\href{https://www.linkedin.com/in/christian-merx-077474116}{christian-merx-077474116}}{\href{mailto:ChristianMerx@gmx.de}{ChristianMerx@gmx.de}}{\href{tel:+4917621940099}{+49 176 21940099}}}

\columnratio{0.65}
\begin{paracol}{2}

\switchcolumn[0]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROFILE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Profile}
\begin{tightemize}
\item Project manager with 10+ years of experience in the automotive sector, including safety-relevant and security-related software development.
\item Strong background in leading cross-functional and multinational teams, aligning stakeholders, and guiding projects from planning through delivery.
\item Rich experience in agile SW development, SPICE-oriented processes, requirements engineering, and customer-facing communication.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{Elektrobit Automotive GmbH}
\descript{| Process Manager for PM Process (MAN.3)}
\location{Apr 2022 -- Jul 2025 | Erlangen, Germany}
\begin{tightemize}
\item Definition, rollout and improvement of PM process and tools for the complete company.
\item A unified process for agile and classical projects was sucessfully introduced.
\end{tightemize}
\sectionsep

\runsubsection{Elektrobit Automotive GmbH}
\descript{| Senior Project Manager}
\location{Apr 2020 -- Jul 2025 | Erlangen, Germany}
\begin{tightemize}
\item Managed automotive software projects from planning through implementation with a strong focus on timely delivery, risk management and customer collaboration.
\item Led cross-functional teams in dynamic environments with on-site test sessions and tight SoP deadlines.
\end{tightemize}
\sectionsep

% \runsubsection{Elektrobit Automotive GmbH}
% \descript{| Project Manager}
% \location{May 2012 -- Mar 2020 | Erlangen, Germany}
% \begin{tightemize}
% \item Successfully delivered navigation, HMI, and ADAS-related software projects for OEM and tier-1 customers.
% \item Coordinated technical and organizational topics across distributed teams and external partners.
% \end{tightemize}
% \sectionsep

% \runsubsection{Elektrobit Automotive GmbH}
% \descript{| Senior Software Developer}
% \location{May 2008 -- Apr 2012 | Erlangen, Germany}
% \begin{tightemize}
% \item Built and maintained software for speech dialog and HMI systems in automotive projects.
% \item Supported customer integration, bug fixing, and feature delivery in close collaboration with OEM teams.
% \end{tightemize}
% \sectionsep

% \runsubsection{3Soft GmbH}
% \descript{| Software Developer}
% \location{Jan 2006 -- Apr 2008 | Erlangen, Germany}
% \begin{tightemize}
% \item Contributed to embedded and HMI-related software development in early career roles.
% \end{tightemize}
% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Selected Projects}

\runsubsection{Security for Diagnosis for VW / Cariad}
\descript{| AUTOSAR Classic}
\location{2021 -- 2025}
\begin{tightemize}
\item Managed the development team for secure diagnosis communication software and aligned OEM, tier-1, and function owners.
\item Successfully used in safety-relevant car control-units (ASIL). Level 2 ASPICE audit passed successfully. Software used in several car lines and brands.
\end{tightemize}
\sectionsep

\runsubsection{Agile AUTOSAR Development for JLR}
\descript{| AUTOSAR Classic}
\location{2022 -- 2024}
\begin{tightemize}
\item Led an agile team delivering AUTOSAR Classic-based car applications and coordinated feature scope with the customer.
\item 4 Submodules delivered on time for the planned SOP.
\end{tightemize}
\sectionsep

\runsubsection{Continental ADAS Radar for Daimler}
\descript{| Radar-based driving functions}
\location{2019 -- 2020}
\begin{tightemize}
\item Managed multiple teams and coordinated delivery, escalations, and on-site test campaigns for complex algorithmic software features.
\item 2 software modules successfully delivered into series software, used in several car models.
\end{tightemize}
\sectionsep

% \runsubsection{BMW Mid Navigation System}
% \descript{| Navigation / database access}
% \location{2015 -- 2018}
% \begin{tightemize}
% \item Supported requirements analysis, planning, and delivery for navigation-related functionality with OEM and tier-1 stakeholders.
% \end{tightemize}
% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\switchcolumn[1]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Management}
\sectionsep
\location{Strengths:}
Project Management and Ownership \textbullet{} Stakeholder Alignment \textbullet{} Team Leadership and mentoring \textbullet{} Customer Communication \textbullet{}
Risk Management \textbullet{} Planning \textbullet{} Escalation Handling \\
\sectionsep
\subsection{Processes and Methods}
\sectionsep
ASPICE \textbullet{} Agile \textbullet{} Scrum \textbullet{} Kanban \textbullet{} Requirements Engineering \textbullet{}
Release Coordination \textbullet{} Process Improvement \\
\sectionsep
\subsection{Technical}
\sectionsep
AUTOSAR Classic \textbullet{} C++ \textbullet{} C \textbullet{} Python \textbullet{} Embedded Software \textbullet{}
Debugging \textbullet{} CI/CD \textbullet{} Automotive Domain Knowledge \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LANGUAGES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Languages}
\begin{tightemize}
\item English: fluent in writing and speaking (C1)
\item German: native speaker
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}
\subsection{Otto-von-Guericke University}
\descript{Dipl.-Ing. Information Technology}
\location{Oct 1998 -- May 2005 | Magdeburg, Germany}
Specialization in Technical Informatics \\
\location{Thesis: Quantification of performance parameters of digital image correction}
\sectionsep

\subsection{Norbertusgymnasium}
\descript{Abitur}
\location{Aug 1991 -- Jul 1997 | Magdeburg, Germany}
Focus on Physics and Mathematics
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     INTERESTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Interests}
\begin{tightemize}
\item Running, hiking and cycling
\item Music, movies and computer games
\end{tightemize}

\end{paracol}
